The Concurrent Calculi Formalisation Benchmark

### 2023-10-11 paper/paper.tex
rework the design of the benchmark section

\section{Design of the benchmark}\label{sec:design-discussion}
In this section, we will describe the considerations we considered during the design of the benchmark challenges.
We will start with some general remarks, then describe the individual design considerations for each challenge problem.

@@

While our challenges require reasoning about binders, which was the main topic of the original POPLMark, they also require other techniques.
Our challenges also require reasoning about logical relations which goes above the reasoning involved in POPLMark Reloaded.

We have decided not to include the choice construct in our challenge problems.
Choice constructs complicate the theory, and our aim is to keep the challenges focused.
For the same reason, each challenge problem only includes the fragment necessary to express the theorems we are interested in with regards to the challenge.
We leave extensions of the syntax for a future benchmark challenge.

Our challenge problems do not include reasoning about encodings, since we do not believe that encodings require any different reasoning techniques in a concurrency setting than in any other setting.

>>>>

\section{Design of the benchmark}\label{sec:design-discussion}
In this section, we outline the factors considered in designing the
benchmark challenges. We start with some general remarks, then
describe the individual design considerations for each challenge
problem.

@@

While our challenges require reasoning about binders, which was the main topic of the original POPLMark, they also require other techniques.
Our challenges also require reasoning about logical relations which goes above the reasoning involved in POPLMark Reloaded.\fxwarning{does it? as in do we define a type indexed
  relation and then use that to prove things?}

The aim of this challenge is to keep the problems focused on the
features we want to exercise. For that reason, we have decided not to
include the choice construct in our challenge problems. Choice
constructs complicate the theory. For the same reason, each challenge
problem only includes the fragment necessary to express the theorems
we are interested in. We leave extensions of the syntax for a future
benchmark challenge.

Our challenge problems do not include reasoning about encodings. While
this kind of reasoning is common in the field, it does not require any
different reasoning techniques in a concurrency setting than in any
other setting.
